Inefficient Concessions and Mediation

### 2019-10-18 notes.tex
add notes on min separating concessions for different values of e

>>>>

\vskip.2in
When $e=1$ and no material value, $g_h^* = p(T+D)$ is the smallest concession for CSE. \\
When $e=1$ and concessions have material value, $g' = \frac{p(1-\de_l)(D+T)}{(1-\de_l)(1-pT) + (1-p)D}$ is the minimum separating concession [Theorem 3]
I claim in Theorem 5 that the minimum separating concession under mediation is $g^* = \frac{g'}{1-p}$.
